An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-05-12 poly-embed-journal/poly-embed-journal.tex
finding my error in prop 4

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
\jessie{ TODO Items 01 Mar 2021
	\begin{itemize}
		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
		\item \sout{Flesh out and expand on Ordered Partition Example}
		\item add paragraph of discussion on the requirements of polyhedral losses
		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
		\begin{itemize}
		\item \sout{for now, move everything up except PDs}
		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
		\end{itemize}
		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
\end{itemize}
TODO Items summer 2020
	\begin{itemize}
		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
		\item Replace Proposition 2 with Lemma 7?
		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
	\end{itemize}}

@@

	Since $r \in \Gamma(p_{r'}^r)$, we have the hyperplane $H_L(p_{r'}^r; r) := \inprod{p_{r'}^r}{L(r)}$ supporting $\risk{L}$ at $p_{r'}^r$, and similarly $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
	\begin{align*}
	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
	\end{align*}
	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
%	\jessie{This is not well-written... nor correct as written?}

@@

\begin{remark}\label{remark:embed-trim}
	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
		\item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
		\item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
	\end{enumerate}
Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ has no duplicate elements such that $\cup \Theta' = \simplex$.
\end{remark}
\begin{proof}[Sketch]
	$(a \implies b)$
	If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.

>>>>

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
%\jessie{ TODO Items 01 Mar 2021
%	\begin{itemize}
%		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
%		\item \sout{Flesh out and expand on Ordered Partition Example}
%		\item add paragraph of discussion on the requirements of polyhedral losses
%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{thm:ie-iff-embeds-refinement} can use a look too.
%		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
%		\begin{itemize}
%		\item \sout{for now, move everything up except PDs}
%		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
%		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
%		\end{itemize}
%		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
%\end{itemize}
%TODO Items summer 2020
%	\begin{itemize}
%		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
%		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
%		\item Replace Proposition 2 with Lemma 7?
%		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
%	\end{itemize}}

@@

	Observe that the hyperplane $H_L(p; u) := p \mapsto \inprod{p}{L(u)}$ supports $\risk{L}$ at $p$ if and only if $r \in \Gamma(p)$.
	By assumption, we have $H_L(p_{r'}^r; r)$ supporting $\risk{L}(p_{r'}^r)$ and $H_L(p_{r''}^r; r)$ supporting $\risk{L}(p_{r''}^r)$.
	As $H_L(\cdot;r)$ is linear in its first argument (this is true for any $r \in \R^*$), then $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.

	Now observe that 
	$r' \in \Gamma(p_{r'}^r) \iff H_L(p_{r'}^r; r')$ supports $\risk{L}(p_{r'}^r)$.
	Since $\risk{L}$ is linear between $p_{r'}^r$ and $p_{r''}^r$, \jessie{THIS IS INCORRECT} it therefore also supports $\risk{L}(p_{r''}^r) \iff r' \in \Gamma(p_{r''}^r)$, yielding a contradiction.

	Therefore, for all $r \in \R^*$, there must be some $p_r$ such that $\Gamma(p_r) = \{r\}$, and thus $\R^*$ is a minimum representative set.

%	Observe that the hyperplane $H_L(p_{r'}^r; r) := p_{r'}^r \mapsto \inprod{p_{r'}^r}{L(r)}$ supports $\risk{L}$ at $p_{r'}^r$ if and only if $r \in \Gamma(p_{r'}^r)$.
%	Similarly, we can conclude $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
%	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
%	\begin{align*}
%	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
%	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
%	\end{align*}
%	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
%%	\jessie{This is not well-written... nor correct as written?}

@@

\begin{remark}\label{remark:embed-trim}
	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
		\item $\Gamma$ has a finite representative set $\U$.\jessie{, and therefore any minimum representative set for $\Gamma$ is also finite.}
		\item There is a finite multiset $\Theta$ full-dimensional level sets of $\Gamma$, and $\cup\, \Theta = \simplex$. 
	\end{enumerate}
Moreover, when $\Gamma$ tightly embeds $\gamma$, $\U$ is a minimum representative set, and there is a $\Theta' \subseteq \Theta$ with no duplicate elements such that $\cup \Theta' = \simplex$.
\end{remark}
\begin{proof}[Sketch]
	$(a \implies b)$
	If $\Gamma$ embeds $\gamma$, then we can take the embedded target reports $\U := \varphi(\R')$ and show this is a finite representative set for $L$.
	We know it is finite as $\R'$ is finite, and consider that $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R'$, hence $\R \cap \gamma(p) \neq \emptyset \implies \varphi(\R) \cap \Gamma(p) \neq \emptyset$ for all $p \in \simplex$.
